Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions

### 2024-07-04 02_paper/02_study/02_eye tracking video questionnaire paper/paper_methods.tex
expertise

In the current study, objectivity of application was ensured by the questionnaire-format, the written instructions and by a detailed test administration manual of the study \emph{ProVisioNET}. The objectivity of analysis was given by processing the obtained questionnaire data in R (Version 4.3.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.50; Andri et mult. al., 2022), \emph{dplyr} (Version 1.1.3; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.4.4; Wickham, 2016), \emph{ggrepel} (Version 0.9.4; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.3; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.45; Xie, 2015), \emph{lme4} (Version 1.1.35.1; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.4; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{sf} (E. Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.15; Lüdecke, 2021), \emph{sp} (E. J. Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tibble} (Version 3.2.1; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.3.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 2.0.0; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.4; M. Barth, 2022), \emph{viridis} (Version 0.6.4; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.2; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) and IBM SPSS 28.

@@

All reported data analyses were conducted with the R (Version 4.3.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.50; Andri et mult. al., 2022), \emph{dplyr} (Version 1.1.3; Wickham et al., 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson et al., 2021), \emph{ggplot2} (Version 3.4.4; Wickham, 2016), \emph{ggrepel} (Version 0.9.4; Slowikowski, 2021), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.3; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.45; Xie, 2015), \emph{lme4} (Version 1.1.35.1; Bates et al., 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.4; Wickham et al., 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.2; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{sf} (E. Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.15; Lüdecke, 2021), \emph{sp} (E. J. Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tibble} (Version 3.2.1; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.3.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 2.0.0; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.4; M. Barth, 2022), \emph{viridis} (Version 0.6.4; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.2; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl et al., 2019) and IBM SPSS 28.

>>>>

In the current study, objectivity of application was ensured by the questionnaire-format, the written instructions and by a detailed test administration manual of the study \emph{ProVisioNET}. The objectivity of analysis was given by processing the obtained questionnaire data in R (Version 4.3.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.3; Wilke, 2020), \emph{DescTools} (Version 0.99.54; Andri et mult. al., 2022), \emph{dplyr} (Version 1.1.4; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson, Hofmann, \& Cook, 2021), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{ggrepel} (Version 0.9.5; Slowikowski, 2021), \emph{ggthemes} (Version 5.1.0; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.4; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.47; Xie, 2015), \emph{lme4} (Version 1.1.35.4; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7.1; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.5; Wickham, Hester, \& Bryan, 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.4; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{sf} (E. Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.16; Lüdecke, 2021), \emph{sp} (E. J. Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tibble} (Version 3.2.1; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.3.1; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 2.0.0; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.4; M. Barth, 2022), \emph{viridis} (Version 0.6.5; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.2; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019) and IBM SPSS 28.

@@

All reported data analyses were conducted with the R (Version 4.3.3; R Core Team, 2021) and the R-packages \emph{ARTofR} (Version 0.4.1; Zhang, 2021), \emph{cowplot} (Version 1.1.3; Wilke, 2020), \emph{DescTools} (Version 0.99.54; Andri et mult. al., 2022), \emph{dplyr} (Version 1.1.4; Wickham et al., 2022), \emph{forcats} (Version 1.0.0; Wickham, 2021), \emph{formattable} (Version 0.2.1; Ren \& Russell, 2021), \emph{ggmosaic} (Jeppson et al., 2021), \emph{ggplot2} (Version 3.5.1; Wickham, 2016), \emph{ggrepel} (Version 0.9.5; Slowikowski, 2021), \emph{ggthemes} (Version 5.1.0; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{haven} (Version 2.5.4; Wickham \& Miller, 2021), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{kableExtra} (Version 1.4.0; Zhu, 2021), \emph{knitr} (Version 1.47; Xie, 2015), \emph{lme4} (Version 1.1.35.4; Bates et al., 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.9.3; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.60.0.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.6.5; Bates \& Maechler, 2021), \emph{moments} (Version 0.14.1; Komsta \& Novomestky, 2015), \emph{msm} (Version 1.7.1; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.2; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{purrr} (Version 1.0.2; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.5; Wickham et al., 2021), \emph{readxl} (Version 1.4.3; Wickham \& Bryan, 2019), \emph{rgeos} (Bivand \& Rundel, 2021), \emph{rlang} (Version 1.1.4; Henry \& Wickham, 2022), \emph{rnaturalearth} (South, 2017a, 2017b), \emph{rnaturalearthdata} (South, 2017b), \emph{sf} (E. Pebesma, 2018), \emph{sjlabelled} (Version 1.2.0; Lüdecke, 2022), \emph{sjPlot} (Version 2.8.16; Lüdecke, 2021), \emph{sp} (E. J. Pebesma \& Bivand, 2005), \emph{stringr} (Version 1.5.1; Wickham, 2019), \emph{tibble} (Version 3.2.1; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.3.1; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 2.0.0; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.4; M. Barth, 2022), \emph{viridis} (Version 0.6.5; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.2; Garnier et al., 2021b), and \emph{xtable} (Version 1.8.4; Dahl et al., 2019) and IBM SPSS 28.
